Cognitive Analysis

### 2024-10-28 Manuscript Analysis/ASHA Poster Analyses.Rmd
updated ple figures

ggsave("Figures/ple_plot.png", plot = last_plot(), width = 3, height = 6, units = "in", scale = 1.2)

@@

```
### Model 9

@@

```
### Model 11

@@

```
### Model 14

@@

The final model take-aways, in reference to the cognitve measures of interest, are:
- The interaction between working memory and speaker: On average, when listening to the speaker with ALS, listeners with higher working memory scores rated effort higher. 
- The interaction between cognitive flexibility and speaker: On average, when listening to the speaker with ALS, listeners with higher cognitive flexibility scores rated effort lower.
- The interaction between working memory and repetition accuracy: On average, listeners with higher working memory scores rated effort phrases they did not accurately recognized lower.
- The interaction between cognitive flexibility and repetition accuracy: On average, listeners with higher cognitive flexibility scores rated effort higher for phrases they did not accurately recognize.
- Teh three way interactions between speaker, repetition accuracy, and each of the cognitve measures was tested. None of these interactions were significant.

>>>>

ggsave("Figures/ple_plot_cog.png", plot = last_plot(), width = 3, height = 6, units = "in", scale = 1.2)

@@

@@

@@

@@

The final model take-aways, in reference to the cognitive measures of interest, are:

-   The interaction between working memory and speaker: On average, when listening to the speaker with ALS, listeners with higher working memory scores rated effort higher.

-   The interaction between cognitive flexibility and speaker: On average, when listening to the speaker with ALS, listeners with higher cognitive flexibility scores rated effort lower.

-   The interaction between working memory and repetition accuracy: On average, listeners with higher working memory scores rated effort phrases they did not accurately recognized lower.

-   The interaction between cognitive flexibility and repetition accuracy: On average, listeners with higher cognitive flexibility scores rated effort higher for phrases they did not accurately recognize.

-   The three way interactions between speaker, repetition accuracy, and each of the cognitive measures was tested. None of these interactions were significant.

### 2024-10-28 Manuscript Analysis/manuscript_analysis.Rmd

ple |>
  dplyr::select(subject, trial, speaker, code, effort_rating, rep_acc, ends_with("_c")) |>
  dplyr::group_by(subject, speaker, rep_acc, list_sort_c, flanker_c, card_sort_c, pattern_c) |>
  dplyr::summarize(effort = mean(effort_rating)) |>
  dplyr::rename('Working Memory' = list_sort_c,
                'Inhibitory Control' = flanker_c,
                'Cognitive Flexibility' = card_sort_c,
                'Processing Speed' = pattern_c) |>
  tidyr::pivot_longer(cols = "Working Memory":"Processing Speed",
                     names_to = "cog_measure",
                     values_to = "score") |>
  ungroup() |>
  ggplot() +
  aes(x = score,
      y = effort,
      color = speaker,
      shape = speaker) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm") +
  facet_grid(rep_acc ~ cog_measure) +
  labs(x = "Score", y = "Perceived Listening Effort Rating") +
  theme_classic() +
  scale_color_manual(values = my_pal) +
  scale_shape_manual(values = c(1, 2)) +
  theme(aspect.ratio = 1)

>>>>

ple |>
  dplyr::select(subject, trial, speaker, code, effort_rating, rep_acc, ends_with("_c")) |>
  dplyr::group_by(subject, speaker, rep_acc, list_sort_c, flanker_c, card_sort_c, pattern_c) |>
  dplyr::summarize(effort = mean(effort_rating)) |>
  dplyr::rename('Working Memory' = list_sort_c,
                'Inhibitory Control' = flanker_c,
                'Cognitive Flexibility' = card_sort_c,
                'Processing Speed' = pattern_c) |>
  tidyr::pivot_longer(cols = "Working Memory":"Processing Speed",
                     names_to = "cog_measure",
                     values_to = "score") |>
  ungroup() |>
  ggplot() +
  aes(x = score,
      y = effort,
      color = speaker,
      shape = speaker) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm") +
  facet_grid(cog_measure ~ rep_acc) +
  labs(x = "Score", y = "Perceived Listening Effort Rating") +
  theme_classic() +
  scale_color_manual(values = my_pal) +
  scale_shape_manual(values = c(1, 2)) +
  theme(aspect.ratio = 1)

ggsave("Figures/ple_plot_cog.png", plot = last_plot())
